---
title: "Fizzbuzz"
author: "Matt"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains student solutions to the fizzbuzz problem. Students will add to this file using the outline below. Write your name (using three hashtags), then below create an R code block and insert your code. Save the .rmd file, then knit the document to update the html output. Then submit a pull request to merge your changes to the main repository.

### Richard Troise

```{r, eval = FALSE}
  vec_num <- c(1:100)

  k <- 1
  while(k <= 100) {    
    if(vec_num[k]%%3==0 || vec_num[k]%%5== 0) {
      if(vec_num[k]%%3==0 && vec_num[k]%%5== 0) {print("FizzBuzz")}
        if(vec_num[k]%%5 == 0) {
          print("Buzz")
          k <- k + 1
        }
        else {
          print("Fizz")
          k <- k + 1
        }
    }
    
      else {
        print(vec_num[k])
        k <- k + 1          
      }

}
```

### Matt's Code

```{r,eval=F}
answer <- 1:100
for(i in 1:100){
  if(i%%3 == 0) answer[i] <-"fizz"
  if(i%%5 == 0) answer[i] <-"buzz"
  if(i%%5 == 0 & i%%3 ==0) answer[i] <-"fizzbuzz"
}
print(answer)
```

